Alone Together: Compositional Reasoning and Inference for Weak Isolation

### 2017-10-22 isolation.tex

\textbf{Snapshot Isolation (SI)} The concept of executing a
transaction against a consistent snapshot of the database was first
proposed as Snapshot Isolation in~\cite{berenson}. SI doesn't admit
write-write conflicts, and the original proposal, which is implemented
in Microsoft SQL Server, required the database to roll-back an SI
transaction if conflicts are detected during the commit. This behavior
can be axiomatized as $\I_e = \I_{ss}$ (execution against a snapshot),
and $\I_c = \I_{ww}$ (avoiding write-write conflicts during the
commit).
% \begin{smathpar}
% \begin{array}{lcl}
% \I_e\,\,(\stl,\stg,\stg') & = & \stg' = \stg\\
% \I_c\,\,(\stl,\stg,\stg') & = & \forall(r\in\stl)(r'\in\stg).~ r'.\idf = r.\idf \Rightarrow r'\in\stg'.
% \end{array}
% \end{smathpar}
Note that the same axiomatization applies to Postgres's RR,
although its implementation (described in Sec.~\ref{sec:motivation})
differs considerably from the original proposal. Thus, reasoning done
for an SI transaction on MS SQL server carries over to Postgres's RR
and vice-versa, demonstrating the benefits of reasoning axiomatically
about isolation properties.

>>>>

\textbf{Snapshot Isolation (SI)} The concept of executing a
transaction against a consistent snapshot of the database was first
proposed as Snapshot Isolation in~\cite{berenson}. SI doesn't admit
write-write conflicts, and the original proposal, which is implemented
in Microsoft SQL Server, required the database to roll-back an SI
transaction if conflicts are detected during the commit. This behavior
can be axiomatized as $\I_e = \I_{ss}$ (execution against a snapshot),
and $\I_c = \I_{ww}$ (avoiding write-write conflicts during the
commit).
% \begin{smathpar}
% \begin{array}{lcl}
% \I_e\,\,(\stl,\stg,\stg') & = & \stg' = \stg\\
% \I_c\,\,(\stl,\stg,\stg') & = & \forall(r\in\stl)(r'\in\stg).~ r'.\idf = r.\idf \Rightarrow r'\in\stg'.
% \end{array}
% \end{smathpar}
Note that the same axiomatization applies to PostgreSQL's RR,
although its implementation (described in Sec.~\ref{sec:motivation})
differs considerably from the original proposal. Thus, reasoning done
for an SI transaction on MS SQL server carries over to PostgreSQL's RR
and vice-versa, demonstrating the benefits of reasoning axiomatically
about isolation properties.
